---
title       : Stock Return Analysis App
subtitle    : Data Science Project Using Slidify
author      : Ren-Huai Huang
job         : Data Scientist Biochemistry Biophisics
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction:  

1. The App is to compare a stock history price to a index price. 

2. The data of the stock price is automatically download from [Yahoo](http://finance.yahoo.com/).

3. The data and the plots will be displayed in corresponding tab in the main panel. 

4. The App is only analysis the monthly data.

--- .class #3
## Instruction (how to use it):

* Input the ticker symbol of a stock that you want to analyze in the inputbox in the left sidebar  

    + you can looking up a ticker sysbol at [Yahoo Finance](http://finance.yahoo.com/lookup)

* Select a stock index in the radioButtons in the left sidebar. There are three selections: 

    + S&P 500 (5EGSPC)

    + Dow Jones Industrial Average (5EDJI)

    + NASDAQ Composite (5EIXIC) 

--- .class #4

## Instruction (continous):

* Look up the tab for the analysis and plot

    + The first tab is the stock price chart which displays the the monthly adjusted close price. 
    
    + The second tab is the most interesting analysis. This tab shows the histogram of yearly countinously compounded  return rate (ccReturn). It is calculated by the following fomula: 
    
    $$ccReturn = \log( (Adj.Close Price) / (Adj.Close Price 13 Month Ago) )$$
    
    + The third tab shows the summary results of both of the stock you inputed and the index that you choosed.
    
    + The bottom of the main panel shows the corresponding tabels download from [Yahoo Finance](http://finance.yahoo.com/lookup)  
    
    + The download address is shown between the tabs and the tables. 


--- .class #5
## Default example to calculate the yearly countinously compounded  return rate (ccReturn):

```{r, echo = F}
library(ggplot2);
```    
```{r}  
stockId = "VGHCX"; yahoo = "http://real-chart.finance.yahoo.com/table.csv?s="
url = paste0(yahoo, stockId, "&g=m&ignore=.csv");
dat <- read.csv(url, header = T, stringsAsFactors=F);  
ccYearRateReturn = log( dat$Adj.Close[1:(nrow(dat)-12)] / dat$Adj.Close[13:(nrow(dat))] ); 
(Mean_ccReturn = round(mean(ccYearRateReturn),4)); 
(STD_ccReturn = round(sd(ccYearRateReturn),4))
```





